---
title: "Final Project"
author: "Mary Buczynski"
date: "4/27/2022"
output: pdf_document
editor_options: 
  chunk_output_type: console
---
#### Insert libraries
```{r}
library(rpart)
library(tree)
library(randomForest)
library(gbm)
library(ROCR)
library(readr)
```

#### Read in library
```{r}
oscars.df <- read_csv("oscars_df - oscars_df.csv")
oscars.df.ex.na <- read_csv("oscars_df - oscars_df.csv")
seed.val<-12345
```

#### Make columns factors
```{r}
oscars.df$Award <- factor(oscars.df$Award)
oscars.df$Consolidated.Genre <- factor(oscars.df$Consolidated.Genre)
oscars.df$Content.Rating <- factor(oscars.df$Content.Rating)
oscars.df$Audience.Status <- factor(oscars.df$Audience.Status)
oscars.df$Tomatometer.Status <- factor(oscars.df$Tomatometer.Status)
```

#### Delete irrelevant/unusable columns and rows
```{r}
oscars.df <- subset(oscars.df, select = -c(...1, Oscar.Year, Film.Studio.Producer.s, Movie.Info, Critic.Consensus, Film.ID, Movie.Genre, Directors, Authors, Actors, Original.Release.Date, Streaming.Release.Date, Production.Company, Tomatometer.Top.Critics.Count, Tomatometer.Fresh.Critics.Count, Tomatometer.Rotten.Critics.Count, Tomatometer.Count, Genres, Film))
oscars.df.ex.na <- oscars.df[!(is.na(oscars.df$Content.Rating) | oscars.df$Content.Rating ==""), ]
```

#### Single Tree
```{r}
set.seed(seed.val)
data.size.tree<-nrow(oscars.df.ex.na)
train.rows.tree<-sample(1:data.size.tree, data.size.tree/2)
train.data.tree<-oscars.df.ex.na[train.rows.tree,]
test.data.tree<-oscars.df.ex.na[-train.rows.tree,]
true.vals.tree<-test.data.tree[, 12]

tree.movies <- tree(Award ~ Movie.Time + Consolidated.Genre + IMDB.Rating + IMDB.Votes + Content.Rating + Tomatometer.Status + Tomatometer.Rating + Audience.Status + Audience.Count, data=train.data.tree)
summary(tree.movies)
plot(tree.movies)
text(tree.movies)
tree.movies
```

#### Pruned Single Tree
```{r}
cv.movies <-cv.tree(tree.movies)
plot(cv.movies$size, cv.movies$dev, type="b")
pruned.tree <- prune.tree(tree.movies, best=6)
plot(pruned.tree)
text(pruned.tree)
pruned.tree
```

#### Time Series of winners & length of movie
```{r}
oscar.winners <- oscars.df[oscars.df$Award == "Winner", ]
movies.vec <- oscar.winners$Movie.Time 
movie.ts <- ts(movies.vec, frequency=1, start=c(1927))
movie.ts.plot <- plot(movie.ts, xlab="Year of Release", ylab="Length of Movie (minutes)", main="Length of Best Picture Winners from 1927 to 2019")
```

#### Boxplots of IMDB Ratings for all movies and oscar winners
```{r}
boxplot(oscar.winners$IMDB.Rating, main="IMDB Rating for Oscar Winning Movies")
boxplot(oscars.df.ex.na$IMDB.Rating, main="IMDB Rating for Oscar Winning & Nominated Movies")
```


#### Random Forest for Movie Attributes
```{r}
movie.attributes.df <- subset(oscars.df.ex.na, select=c("Award", "Movie.Time", "Consolidated.Genre", "Content.Rating"))

data.size.rf <- nrow(movie.attributes.df)
train.rows.rf <- sample(1:data.size.rf, data.size.rf/2)
train.data.rf <- movie.attributes.df[train.rows.rf,]
test.data.rf <- movie.attributes.df[-train.rows.rf,]
true.vals.rf <- test.data.rf[,1]

tree.attributes <- tree(Award ~ Movie.Time + Consolidated.Genre + Content.Rating, train.data.rf)
plot(tree.attributes)
text(tree.attributes)
pruned.attributes <- prune.tree(tree.attributes, best=5)
plot(pruned.attributes)
text(pruned.attributes)

rf.movie.att <- randomForest(Award ~., data=train.data.rf, mtry=3, importance=TRUE)
rf.pred <- predict(rf.movie.att, newdata=test.data.rf)
importance(rf.movie.att)
varImpPlot(rf.movie.att)
```

#### Random Forest for Movie Ratings
```{r}
movie.ratings.df <- subset(oscars.df.ex.na, select=c("Award", "IMDB.Rating", "Tomatometer.Status", "Tomatometer.Rating", "Audience.Rating", "Audience.Status"))
movie.ratings.df <- movie.ratings.df[!(is.na(movie.ratings.df$Audience.Status) | movie.ratings.df$Audience.Status ==""), ]

data.size.rf.rate <- nrow(movie.ratings.df)
train.rows.rf.rate <- sample(1:data.size.rf.rate, data.size.rf.rate/2)
train.data.rf.rate <- movie.ratings.df[train.rows.rf.rate,]
test.data.rf.rate <- movie.ratings.df[-train.rows.rf.rate,]
true.vals.rf.rate <- test.data.rf.rate[,1]

rf.movie.rate <- randomForest(Award ~., data=train.data.rf.rate, mtry=5, importance=TRUE)
rf.pred <- predict(rf.movie.rate, newdata=test.data.rf.rate)
importance(rf.movie.rate)
varImpPlot(rf.movie.rate)
```

### Logistic Regression for Ratings Data
```{r}
mod.all.rate <- glm(Award ~ ., family = binomial(logit), data = movie.ratings.df)
summary(mod.all.rate)
mod.step.rate <- step(mod.all.rate)
summary(mod.step.rate)
```

#### Logistic Regression for Attributes Data
```{r}
mod.all.att <- glm(Award ~ ., family = binomial(logit), data = movie.attributes.df)
summary(mod.all.att)
mod.step.att <- step(mod.all.att)
summary(mod.step.att)
```


